Benefits and risks of diversification for individual fishers

### 2017-02-11 portfolio/text/anderson-etal-rev-pfx.tex
Edits

% 250:
\begin{abstract}
Individuals relying on the extraction of natural resources for their
livelihood face high
levels of income variability driven by a mix of environmental, biological,
management, and
economic factors. Key to managing these industries is identifying
how regulatory actions and individual behaviour affect income variability and, by
extension, economic stability and the sustainable use of natural resources. In
commercial fisheries, communities and vessels fishing a greater diversity of
species have less revenue variability than those fishing fewer species.
However, it is unclear if these benefits extend to the actions of individual
fishers and how year-to-year changes in diversification affect revenue and
revenue variability. Here, we evaluate two axes by which fishers in Alaska
can diversify fishing
activities. We show that, despite increasing specialization over the last 30
years, fishing a set of permits with higher species diversity reduces individual revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of existing permits has a fishery-dependent effect on revenue and is
usually (87\% probability) associated with increased revenue uncertainty
the following year. Our results demonstrate that the most effective option for
individuals to decrease revenue variability is to
participate in additional or more diverse fisheries. However, this option is
expensive, often limited by regulations such as license limitation or catch share programs, and
consequently unavailable to many individuals. With increasing climatic variability,
it will be particularly important that
individuals relying on natural resources for their livelihood have effective
strategies to reduce income variability.
 % (`r g2_dens`% probability)
\end{abstract}

>>>>

% 250:
\begin{abstract}
Individuals relying on the extraction of natural resources for their
livelihood face high
levels of income variability driven by a mix of environmental, biological,
management, and
economic factors. Key to managing these industries is identifying
how regulatory actions and individual behaviour affect income variability and, by
extension, economic stability and the sustainable use of natural resources. In
commercial fisheries, communities and vessels fishing a greater diversity of
species have less revenue variability than those fishing fewer species.
However, it is unclear if these benefits extend to the actions of individual
fishers and how year-to-year changes in diversification affect revenue and
revenue variability. Here, we evaluate two axes by which fishers in Alaska
can diversify fishing
activities. We show that, despite increasing specialization over the last 30
years, fishing a set of permits with higher species diversity reduces individual revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of existing permits has a fishery-dependent effect on revenue and is
usually (87\% probability) associated with increased revenue uncertainty
the following year. Our results demonstrate that the most effective option for
individuals to decrease revenue variability is to
participate in additional or more diverse fisheries. However, this option is
expensive, often limited by regulations such as catch share programs, and
consequently unavailable to many individuals. With increasing climatic variability
it will be particularly important that
individuals relying on natural resources for their livelihood have effective
strategies to reduce income variability.
% (`r g2_dens`% probability)
\end{abstract}
